Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-06 paper/paper.tex
restored feature

\begin{compactdesc}
\item[Character $n$-grams] The number of character 1-, 2-, and
  3-grams. 69.94\%.
\item[Frequent character $n$-grams] Only those character $n$-grams
  that are observed more than $m$ times in the corpus are
  considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
\item[Document length] The number of tokens in the text. 11.81\%.
\item[Pronouns] The number of each pronoun. 22.81\%.
\item[Punctuation] The number of each punctuation mark. 27.41\%.
\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the authors L1. We use the counts (???) of the first
  and last three words in each sentence as features. 53.03\%.
\item[Cohesive markers] These are 40 function words (and short phrases)
  that have a strong discourse function in texts \nt{such as 'however', 'becuase', 'in fact' etc}, contributing to its
  cohesiveness. 25.71\%. \nt{Translators tend to spell out implicit utterances and render them explicitly in the target text (REFERENCE TO BLUM-KULKA); MAYBE APPEND THE LIST IN THE END?} 
\item[Cohesive verbs] \nt{This is a list of manually compiled verbs that serve, like `cohesive markers' to spell out implicit utterances; they include, among others, `indicating', `implying' and `containing'. Same, consider appending the list}. 22.85\%.
\item[Function words] The number of occurrences of each word from a
  pre-defined list of 100 \nt{did you use only 100? it should be 400 and the reference should be to Koppel and Ordan} most frequent words in English (excluding
  punctuation). 42.47\%.
\item[Contextual function words, bigrams] Pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. 62.79\%
\item[Contextual function words, trigrams] Same as above, but counting
  \nt{2- or} 3-grams consisting of one or two function words (respectively) and the POS tag of the third word \nt{character?} in the \nt{2- or} 3-gram. 62.32\%.
\item[Lemmas] \nt{these should be actually `stems' as produced by the Stanford tagger} The number of each of the most frequent lemmas in the
  text. ???. 58.95\%.
\item[Prompt] Conjunction of the character $n$-gram features defined
  above with the prompt; since the prompt contributes information on
  the domain, it is likely that some words (and, hence, character
  sequences) will occur more frequently with some prompts than with
  others. 65.09\%.
\item[Misspelling features] ???. 37.29\%.
\item[Brown] ???
\item[Restored] ???
\end{compactdesc}

>>>>

\begin{compactdesc}
\item[Character $n$-grams] The number of character 1-, 2-, and
  3-grams. 69.94\%.
\item[Frequent character $n$-grams] Only those character $n$-grams
  that are observed more than $m$ times in the corpus are
  considered. ??? \nt{this includes 1 to 4 $n$-grams, resulting in 74.12\%}
\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.
\item[Document length] The number of tokens in the text. 11.81\%.
\item[Pronouns] The number of each pronoun. 22.81\%.
\item[Punctuation] The number of each punctuation mark. 27.41\%.
\item[Passives] The ratio of verbs to passive verbs. 12.26\%.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the authors L1. We use the counts (???)\yt{counts for first two and last three words before the period} of the first
  and last three words in each sentence as features. 53.03\%.
\item[Cohesive markers] These are 40 function words (and short phrases)
  that have a strong discourse function in texts \nt{such as 'however', 'becuase', 'in fact' etc}, contributing to its
  cohesiveness. 25.71\%. \nt{Translators tend to spell out implicit utterances and render them explicitly in the target text (REFERENCE TO BLUM-KULKA); MAYBE APPEND THE LIST IN THE END?} 
\item[Cohesive verbs] \nt{This is a list of manually compiled verbs that serve, like `cohesive markers' to spell out implicit utterances; they include, among others, `indicating', `implying' and `containing'. Same, consider appending the list}. 22.85\%.
\item[Function words] The number of occurrences of each word from a
  pre-defined list of 100 \nt{did you use only 100? it should be 400 and the reference should be to Koppel and Ordan} \yt{we used 100. differences between 100 and >100 were insignificant} most frequent words in English (excluding
  punctuation). 42.47\%.
\item[Contextual function words, bigrams] Pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. 62.79\%
\item[Contextual function words, trigrams] Same as above, but counting
  \nt{2- or} 3-grams consisting of one or two function words (respectively) and the POS tag of the third word \nt{character?} in the \nt{2- or} 3-gram. 62.32\%.
\item[Lemmas] \nt{these should be actually `stems' as produced by the Stanford tagger} The number of each of the most frequent lemmas in the
  text. ???. 58.95\%.
\item[Prompt] Conjunction of the character $n$-gram features defined
  above with the prompt; since the prompt contributes information on
  the domain, it is likely that some words (and, hence, character
  sequences) will occur more frequently with some prompts than with
  others. 65.09\%.
\item[Misspelling features] ???. 37.29\%.
\item[Brown] ???
\item[Restored] \yt{Counts of substitutions, deletions and insertions of predefined tags that we restored in essays edited with a spelling  corrector and missing all these tags. We define three types of tags: (1) punctuation marks (same list as for punctuation feature), (2) function words (WH-words, prepositions, conjunctions, articles, auxiliary verbs, quantifiers, personal pronouns, possessive pronouns, quantified pronouns), (3) cohesion verbs (lemma, present contiguous/progressive and present simple for each verb). We first remove these tags from texts and then recover the most likely hidden tags in a sequence of words, according to an N-gram language model trained on all essays in the training corpus corrected with a spell checker and containing both words and hidden tags. This feature should capture specific words or punctuation marks that are consistently omitted (deletions), or misused (insertions, substitutions).  To restore hidden tags we use hidden-ngram utility provided in SRILM toolkit\footnote{http://www.speech.sri.com/projects/srilm/manpages/hidden-ngram.1.html} (ref to SRILM). 47.67\%}

\end{compactdesc}
